#Savitzky Golay: find best settings for outlier detection
SKR, AQF, sep2016:   
Input:  
- outliers to be identified   
- ranges for each parameter to be used for outlier detection (here: distanceCrit, width, polynomial degree)   
Output:   
- table of perfect fits (only the outliers identified by the user are identified by the algorithm - not more, not less)   
- table of all detection results   best


#Load and prepare data
Load data as xts object:
```{r}
ts<-readRDS('data_broekelei_pump_turbidity.rds')
```

Reduce data and round date to full minutes:

```{r,message=FALSE}
require("xts")
time(ts) <- round(time(ts), "mins")
ts<-xts::first(ts, n=1440/2)
ts<-xts::last(ts, n=300)
```

#Reference time series of outliers
These are the points I want R to identify as outliers:
```{r}
# EDIT THIS WHEN EDITING YOUR DATA (ts):
refOutlierTimestamps <- c('2015-04-20 07:25','2015-04-20 08:43','2015-04-20 09:41', '2015-04-20 10:20', '2015-04-20 10:40', '2015-04-20 10:59')

numberOfOutliersToFind <- length(refOutlierTimestamps)
# get comparable time formats and use later for comparison with result xts:
refOutlierTimestamps <- xts(matrix(TRUE, ncol=1, nrow=length(refOutlierTimestamps)), as.POSIXct(refOutlierTimestamps, tz = "GMT", origin = "1970-1-1"))
time(refOutlierTimestamps) <- round(time(refOutlierTimestamps), "mins")

flag <- which(time(ts) %in% time(refOutlierTimestamps))
refOutliers = ts
mode(refOutliers) <- "logical";
refOutliers[flag] <- FALSE
refOutliers[-flag] <- TRUE

require("m181")
m181::visualise_dy(ts, refOutliers)
```


#Identify outliers and compare to the reference outliers:

```{r}
require("prospectr")#savitzky golay

distanceCritSeq <- seq(20, 120, 5)
widthSeq <- seq(1, 71, 2)
polynomialDegreeSeq <- seq(0, 11, 1)

setNo <- 0
allSets <- NULL
for (distanceCrit in distanceCritSeq) {
  for (width in widthSeq) {
    for (polynomialDegree in polynomialDegreeSeq){
      setNo <- setNo + 1
      correct <- NA
      falsePositive <- NA
      falseNegative <- NA
      if (polynomialDegree<width) {
        smoothTs <- t(savitzkyGolay(t(as.data.frame(ts)), p=polynomialDegree, w=width, m=0))
        smoothTs<-xts(smoothTs,as.POSIXct(rownames(smoothTs), tz = "GMT", origin = "1970-1-1"))
        names(smoothTs) <- 'smoothTs'
        
        #align time (savitzkyGolay cuts the first elements) by adding dummy data:
        tmpIndex <- 1:((width-1)/2)
        dummyData <- ts[tmpIndex, ]
        dummyData[ ,1] <- NA
        smoothTs <- rbind(smoothTs, dummyData)
        
        flag <- which(abs(ts - smoothTs) > distanceCrit)
        my.outlier = ts
        mode(my.outlier) <- "logical";
        my.outlier[flag] <- FALSE
        my.outlier[-flag] <- TRUE
        
        #require("m181")
        #m181::visualise_dy(ts, my.outlier)
        
        identified_correct <- my.outlier[which((!my.outlier) & (!refOutliers))]
        # false alarm (identified, but shouldn't have heen):
        identified_falsePositive <- my.outlier[which((!my.outlier) & refOutliers)]
        # missing alarm (not identified, but should have heen):
        identified_falseNegative <- my.outlier[which(my.outlier & (!refOutliers))]
        
        correct <- length(identified_correct)
        falsePositive <- length(identified_falsePositive)
        falseNegative <- length(identified_falseNegative)
      }
      # total detection errors: 0 would be perfect
      detectionErros <- (numberOfOutliersToFind-correct) + falsePositive + falseNegative
      
      # collect data:
      newSet <- cbind(setNo, detectionErros, distanceCrit, width, polynomialDegree, correct, falsePositive, falseNegative)
      allSets <- rbind(allSets, newSet)
    }
  }
}
```


#Perfect fits:

```{r}
#reduce allSets to perfect fits:
copyIndex <- which(0==allSets[, 2])
copyIndex <- copyIndex[!is.na(copyIndex)]
perfectFits <- allSets[copyIndex, ]

library(knitr)
kable(perfectFits, digits=1)

df<-data.frame(perfectFits)
hist(df$distanceCrit)
hist(df$width)
hist(df$polynomialDegree)
```


#All data:

```{r}

kable(allSets, digits=1)


# anybody got ideas for plotting overviews of the results here?

#corrRatio <- matrix(allSets, nrow = length(widthSeq), byrow = FALSE)/numberOfOutliersToFind
#falsePositiveRatio <- matrix(falsePositive, nrow = length(widthSeq), byrow = FALSE)/numberOfOutliersToFind
#falseNegativeRatio <- matrix(falseNegative, nrow = length(widthSeq), byrow = FALSE)/numberOfOutliersToFind


#require("plot3D")
#hist3D(widthSeq, polynomialDegreeSeq, corrRatio, xlab='polynomialDegree', ylab='width', zlab='ratio of correct values',  ticktype = "detailed")
```

