#Load and prepare data
Load data as xts object:
```{r}
ts<-readRDS('data_broekelei_pump_turbidity.rds')
```

Reduce data

```{r}
require("xts")
ts<-xts::first(ts, n=1440/2)
ts<-xts::last(ts, n=300)

```

# M181 routines

Use m181 library and the required plotting library dygraph:
```{r message=FALSE}
require("m181")
require("dygraphs")
```
***


Check for and visualize constancy:
```{r}
absDiff<-abs(diff(ts[!is.na(ts)]))
minStepSize<-min(absDiff[!absDiff==0])
constantValues<-m181::check_constancy(ts, delta_max=minStepSize, relative=FALSE, width=3)
# this still requires to 'invert' the result for plotting!:
constantValues<-!constantValues
m181::visualise_dy(ts, constantValues)
```

***

Check for and visualize outliers:
```{r}
outliers<-m181::check_outlier(ts, sigma_multiplier=2.97875, width=11, moving_window=TRUE, type="mean", verbose=FALSE)
m181::visualise_dy(ts, outliers)
```

***

Check for and visualize range:
```{r}
outsideRange<-m181::check_range(ts, y_min = 0, y_max = 400)
m181::visualise_dy(ts, outsideRange)
```

***

Check for and visualize gradient:
```{r}
gradient<-m181::check_gradient(ts, delta_max = 300)
m181::visualise_dy(ts, gradient)
```
First value of timeseries is always flagged as exceeding gradient.

***

Check for and visualize sign:
```{r}
signChanges<-m181::check_sign_change(ts, width=3, max_changes = 2)
m181::visualise_dy(ts, signChanges)
```

***





# Questions
## NA
As a first step, remove all NA from the time series:
(Is this advisable? Or not? Why?)
```{r}
ts<-ts[m181::check_na(ts)]
```

## Equidistance
What really is percentage here?:
```{r}
m181::check_equidistance(ts, percentage=0.5)
```
So it's not equidistant. Is this information a prerequisite for other routines?

## Noise
Would you use noise detection for these data?:
Check for and visualize noise:
```{r}
noise<-m181::check_noise(ts, s_max=3, width=5, moving_s_max=TRUE)
m181::visualise_dy(ts, noise)
```
If so, how would you parameterize it?

## MAD outlier
How to tune this?:
```{r}
madOutlier<-m181::check_mad_outlier(ts, width=3, multiplier=1, constant=1)
m181::visualise_dy(ts, madOutlier)
madOutlier<-m181::check_mad_outlier(ts, width=3, multiplier=10, constant=1)
m181::visualise_dy(ts, madOutlier)
madOutlier<-m181::check_mad_outlier(ts, width=3, multiplier=1, constant=10)
m181::visualise_dy(ts, madOutlier)
madOutlier<-m181::check_mad_outlier(ts, width=3, multiplier=10, constant=10)
m181::visualise_dy(ts, madOutlier)
```
In the last figure, the biggest outlier is not detected.
Some info on MAD:
http://eurekastatistics.com/using-the-median-absolute-deviation-to-find-outliers

## Sign

Is sign change really a change of sign, or rather a change of sign of diff(ts)?




# Errors
## Gaps
m181::check_gaps(ts)
results in:
Error in data.frame(v_gaps_start, v_gaps_end, v_delta_t, type = "value_gap",  : 
arguments imply differing number of rows: 0, 1

## Plotting
Not finding any false flags is not an option when plotting:
outsideRange<-m181::check_range(ts, 0, 9e99)
m181::visualise_dy(ts, outsideRange)
  Error in `[.xts`(data, , 2) : subscript out of bounds
  